Nonparametric Goodness-of-Fit Tests for Discrete Null Distributions

### 2011-08-25 rjournal/AE.tex
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/ks-test@72 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{fig1.pdf}
\end{center}
\caption{Plot of calculated $p$-values for given test statistics
using numerical integration
(red) compared to the conservative chi-squared bound (dashed blue). 
The null distribution is uniform on the set $\{1,2,3\}$ in this example.
The sharp variations in the calculated $p$-values are a result of numerical
instabilities, and the true $p$-values are bounded by the blue dashed curve.}
\label{cvmissues}
\end{figure}

@@

Functions \code{ks.test()} and \code{cvm.test()} are provided for
convenience in packages \pkg{ks.test} and \pkg{cvm.test}, respectively.
Function \code{ks.test()} offers a revision of
R's Kolmogorov-Smirnov function \code{ks.test()} from base
package \pkg{stats}, while \code{cvm.test()} is a new
function for Cram\'{e}r-von Mises tests.
Both are available from the authors
or from R-Forge (\url{https://r-forge.r-project.org/R/?group_id=802});
\code{ks.test()} will be proposed for inclusion in recommended
package \pkg{stats}.

>>>>

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{fig1.pdf}
\end{center}
\caption{Plot of calculated $p$-values for given test statistics
using numerical integration
(red) compared to the conservative chi-squared bound (dashed blue) and
the Markov inequality bound (dashed green). 
The null distribution is uniform on the set $\{1,2,3\}$ in this example.
The sharp variations in the calculated $p$-values are a result of numerical
instabilities, and the true $p$-values are bounded by the dashed curves.}
\label{cvmissues}
\end{figure}

@@

Functions \code{ks.test()} and \code{cvm.test()} are provided for
convenience in package \pkg{dgof}, available on CRAN.
Function \code{ks.test()} offers a revision of
R's Kolmogorov-Smirnov function \code{ks.test()} from recommended
package \pkg{stats}; \code{cvm.test()} is a new
function for Cram\'{e}r-von Mises tests.
